MRD_final_microbiome

### 2019-06-19 GlobalMicrobiome_NS.Rmd
updated

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("/omega/1006") 
```

##### FUNCTIONS ########

##### Normalization #######

@@

Atlas1006
https://rdrr.io/github/microbiome/microbiome/man/atlas1006.html
Using dataset: atlas1006: HITChip Atlas with 1006 Western adults
This data set contains genus-level microbiota profiling with HITChip for 1006 western adults with no reported health complications. 
Format: phyloseq-class format
Usage: data(atlas1006)

@@

#The phyloseq package seeks to address issues with multiple microbiome analysis packages by providing a set of functions that internally manage the organizing, linking, storing, and analyzing of phylogenetic sequencing data. In general, this package is used for UniFrac analyses.
library(phyloseq)
library(microbiome)
library(knitr)
library(ggpubr)

  #library(phylogeo)
library(dplyr)

#Graphing package used in phyloseq. To edit the default setting of a plot, you need to use functions in this package.
library(ggplot2)

library(viridis) 
library(cowplot)

# install.packages("devtools")
library(devtools)
# install_github("opisthokonta/tsnemicrobiota")
library(tsnemicrobiota)

# Data from http://dx.doi.org/10.1038/ncomms7342
data(atlas1006)   
pseq <- baseline(atlas1006) # only uses the baseline samples. This is n=1006

@@

# Create mnd variable
# grabs the nationality from phyloseq
mbnational <- get_variable(pseq, "nationality" )
# check you've installed this library
library(forcats)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = '~/globalmicrobiome')

#test
```

```{r functions}

##### FUNCTIONS ########
##### Normalization #######

@@

@@

#The phyloseq package seeks to address issues with multiple microbiome analysis packages by providing a set of functions that internally manage the organizing, linking, storing, and analyzing of phylogenetic sequencing data. In general, this package is used for UniFrac analyses.
library(phyloseq)
library(microbiome)
library(knitr)
library(ggpubr)
#library(phylogeo)
library(dplyr)
#Graphing package used in phyloseq. To edit the default setting of a plot, you need to use functions in this package.
library(ggplot2)
library(viridis) 
library(cowplot)
# install.packages("devtools")
library(devtools)
# install_github("opisthokonta/tsnemicrobiota")
library(tsnemicrobiota)
# check you've installed this library
library(forcats)

# Data from http://dx.doi.org/10.1038/ncomms7342
#This data set contains genus-level microbiota profiling with HITChip for 1006 western adults with no reported health complications.

pseq <- baseline(atlas1006) # only uses the baseline samples. This is n=1006

@@

# Create mnd variable
# grabs the nationality from phyloseq
mbnational <- get_variable(pseq, "nationality" )
